Recipient plant traits are important determinants of the impacts of heterospecific pollen upon plant reproduction

### 2019-03-15 Manuscript_draft/Manuscript_draft.Rmd
markdown I hate you

>>>>

I haven't add this to the draft yet but when I look just Solanaceae species, interestingly seems to be a negative trend with style length and heterospecific pollen effect. Curiously, Capsicum and tomato are the ones that are more affected by hp and both have the shortest stigma and style.
The stigma results of tomato are supported by the plot of effct sizes per family where convolvulaceae has a greater negative effect than the other two families (and they are the ones with bigger pollen size)

Here I show the plot of just solanaceae and then with all the species. I have gouped all the treatments, if not I feel like we are doing p hacking with all the analysis, because is increasing the strength of each point 9 times.
```{r, echo=FALSE,fig.align='center',message=FALSE, warning=FALSE, cache=FALSE}
#Here I'm going to perform the analysis per family
#load libraries
library(vegan)
library(nlme)
library(dplyr)
library(reshape2)
#load data
matrix_scale_effect <- readRDS("Data/matrix_scale_effect.Rda")
matrix_effect_size <- readRDS("Data/matrix_effect_size.RData")
traits_all <- read.csv("Data/traits_all.csv", sep=",")
rownames(traits_all) <- rownames(matrix_scale_effect)
si_index <- readRDS("Data/si_index.RData")
traits_all$si_index <- si_index
load("Data/effect_size_all.RData")
effect_size=melt(matrix_effect_size)
####
####SOLANACEAE####
####
matrix_soly=matrix_scale_effect[c(3,7,9,10),c(3,7,9,10)]
matrix_soly=matrix_effect_size[c(3,7,9,10),c(3,7,9,10)]

traits_sola=traits_all[c(3,7,9,10),-c(1,2)]
traits_sola_dist <- dist(traits_sola, diag = T)
a <- mantel(matrix_soly,traits_sola_dist)
summary(a)
mantel(matrix_soly,dist(traits_sola[,2]))
cor.test(sola$Cohen_d,sola$pollen_size)

traits_sola$species <- c("CAAN", "PEIN","SOLY","SOME")
effect_size_sola=effect_size_all[c(1:4),c(1,2)]
effect_size_sola$species <- c("SOME", "SOLY","PEIN","CAAN")
sola <- merge(effect_size_sola,traits_sola,by="species")
sola$style_length<- sola$style_length/1000
cor.test(sola$Cohen_d,sola$style_length)
library("ggpubr")
ggscatter(sola, x = "Cohen_d", y = "style_length", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Hedges' g", ylab = "Style length (mm)", main="A) Solanaceae")

### 2019-03-15 Manuscript_draft/Manuscript_draft.tex
markdown I hate you

>>>>

I haven't add this to the draft yet but when I look just Solanaceae
species, interestingly seems to be a negative trend with style length
and heterospecific pollen effect. Curiously, Capsicum and tomato are the
ones that are more affected by hp and both have the shortest stigma and
style. The stigma results of tomato are supported by the plot of effct
sizes per family where convolvulaceae has a greater negative effect than
the other two families (and they are the ones with bigger pollen size)

Here I show the plot of just solanaceae and then with all the species. I
have gouped all the treatments, if not I feel like we are doing p
hacking with all the analysis, because is increasing the strength of
each point 9 times.
